Bioverse: Origins of Life

### 2024-06-20 src/tex/ms.tex
only one theoretical experiment conducted

%\subsection{H1: Life only originates in hydrothermal vents}
%The hydrothermal vent scenario does not allow oceans deep enough to form an impenetrable layer of high-pressure ice on its floor.
%The resulting allowed parameter space is described by a lower limit on the bulk density. \todo[inline]{+ exclude atmospheric signature for water worlds?}
%...
%
%\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}
%We parametrize the required exposed land surface in this scenario as a lower limit in bulk density that is higher than for H1.
%Further, the tidal locking timescale of the planet may not be smaller than the age of the system.
%...
%
%\subsection{H3: Life only originates on planets with particular UV irradiance}
\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.

>>>>

%\subsection{H1: Life only originates in hydrothermal vents}
%The hydrothermal vent scenario does not allow oceans deep enough to form an impenetrable layer of high-pressure ice on its floor.
%The resulting allowed parameter space is described by a lower limit on the bulk density. \todo[inline]{+ exclude atmospheric signature for water worlds?}
%...
%
%\subsection{H2: Life only originates in subaerial ponds with wet/dry cycles}
%We parametrize the required exposed land surface in this scenario as a lower limit in bulk density that is higher than for H1.
%Further, the tidal locking timescale of the planet may not be smaller than the age of the system.
%...
%
%\subsection{H3: Life only originates on planets with particular UV irradiance}
\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}
Here, we conduct a theoretical experiment on the UV irradiance requirement (Sect.~\ref{sec:predictions}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
